Simulation Modeling of Glycosylation Effects on Potassium Channels of Mouse Cardiomyocytes

### 2021-06-21 draft.tex
Draft 7

% === ABSTRACT ==========================================================
% =======================================================================
\begin{abstract}
Cardiovascular disease is a leading cause of death worldwide. Dilated cardiomyopathy (DCM) is the third most common cause of heart failure and the most frequent reason for heart transplantation; upward of 70\% of DCM cases are considered idiopathic. We showed, through in-vitro experiments, that reduced hybrid/complex N-glycosylation in mouse cardiomyocytes is sufficient to cause DCM. Further, we investigated the role of reduced complex N-glycosylation in the gating and activities of voltage-gated ion channels, specifically, $\text{Na}^{+}$ ($\text{Na}_{v}$), $\text{Ca}^{2+}$ ($\text{Ca}_{v}$), and $\text{K}^{+}$ ($\text{K}_{v}$) channels responsible for ventricular myocyte action potentials (APs). In addition to direct effects of reduced N-glycosylation on $\text{Na}_{v}$ and $\text{Ca}_{v}$ gating, we observed aberrant electrical signalings such as prolonged APs and abnormal early re-activations, consistent with an observed reduction in $\text{K}_{v}$ expression and activity. However, it is difficult to rigorously determine the effects of reduced hybrid/complex N-glycosylation on $\text{K}_{v}$ activity, as there are multiple isoforms in the mouse ventricle including, $\text{K}_{v}1.5$, $\text{K}_{v}2.1$, and $\text{K}_{v}4.2$, that collectively produce the repolarizing phase of the AP. Experimentally, because of the unique inactivation kinetics of $\text{K}_{v}$ isoforms, only the sum of $\text{K}^{+}$ currents ($\text{I}_{Ksum}$) can be recorded and decomposed using exponential fitting to estimate component currents flowing through $\text{K}_{v}$ isoforms. However, such decomposition cannot describe effectively the mechanism of $\text{K}_{v}$ under different glycosylation conditions. Here, we propose to develop simulation models for dominant $\text{K}^{+}$ currents in mouse ventricular myocytes and calibrate their parameters using the in-vitro data under normal and reduced glycosylation conditions through ablation of the Mgat1 gene. Calibrated models help describe key characterisitcs of glycosylation effects and data recorded from in-vitro experiments. A novel model calibration procedure is proposed to deal with complex ionic current models based on nonlinear functions and differential equations. Experimental results show that the proposed method has strong potential to calibrate complex simulation models with sparse data and predict characteristics of multiple $\text{K}_{v}$ isoforms to understand detailed kinetics.
\end{abstract}

% === KEYWORDS ==========================================================
% =======================================================================
\begin{IEEEkeywords}
Electrophysiology, N-glycosylation, dilated cardiomyopathy, voltage-gated potassium channel, simulation modeling, genetic algorithm. 
\end{IEEEkeywords}

@@

Thus, we investigated the impact of reduced hybrid/complex N-glycosylation through the lens of electrophysiology. Electrophysiology refers to studies of electrical properties in cells, tissues, or organs, including the examination of voltage, currents, and changes in scales from ion channels to organ systems \cite{scanziani2009electrophysiology}. Electrical signaling in the heart has vital functions related to intra and extracellular communication, rhythmicity of heartbeats, and provides a driving force for contraction. The action potential (AP) is the net transmembrane potential varying over time which results from the composite activities of different ion channels \cite{grant2009cardiac}. Fig. 1-(a) shows the simulated AP of a mouse ventricular apex myocyte using models adopted from \cite{bondarenko2004computer}. The AP is the result of orchestrated activities of various ionic currents described in Fig. 1-(b). Even small changes in VGIC's function can contribute to aberrant AP waveform and/or conduction, leading to arrhythmias. As illustrated in Fig. 2, voltage-gated $\text{Na}^{+}$ channels ($\text{Na}_{v}$) are responsible for AP initiation, or the depolarization phase, voltage-gated $\text{Ca}^{2+}$ channels ($\text{Ca}_{v}$) are responsible for the prolonged depolarization phase particularly in larger species (“plateau”), while several voltage-gated $\text{K}^{+}$ channel ($\text{K}_{v}$) isoforms are collectively responsible for AP deactivation, i.e., repolarization. Like most transmembrane proteins, VGICs are heavily glycosylated membrane proteins \cite{ednie2011modulation}. Studies have proven that glycosylation can affect VGIC function predominantly. For example, we reported that a saturating, electrostatic effect of negatively charged sialic acids, which are typically attached to the terminal of glycan branches, significantly altered cardiac electrical signaling \cite{ednie2013expression, ednie2015reduced}. Our recent studies observed aberrant electrical signaling, e.g., prolonged APs and abnormal early re-activations, in Mgat1KO ventricular apex myocytes \cite{ednie2019reduced, ednie2019reduced2}. These observations strongly support direct and disease-related effects of reduced N-glycosylation on VGIC gating and activity.
\begin{figure}
    \label{fig1}
    \centering
    \subfloat[]{\includegraphics[width=0.8\linewidth]{photo/sim_ap.png}}
    \\
    \subfloat[]{\includegraphics[width=0.8\linewidth]{photo/sim_currents.png}}
    \caption{Simulation results of the (a) action potential and (b) relevant ionic currents (i.e., $\text{I}_{Kto}$, $\text{I}_{Kslow}$, $\text{I}_{Kss}$, $\text{I}_{Na}$, and $\text{I}_{CaL}$) of mouse ventricular myocytes. Potassium currents have positive currents, while sodium and calcium currents are negative.}
\end{figure}

\begin{figure}
    \label{fig2}
    \centering
    \includegraphics[width=0.8\linewidth]{photo/ap_ion_channels.png}
    \caption{Predominant ion channels in human ventricular myocytes and their functional role in shaping an AP}
    \label{fig:my_label}
\end{figure}

Although these in-vitro experiments showed changes in activities of ion channels, there are certain limitations that include: 1) \textit{Detailed ion channel kinetics are difficult to determine rigorously using in-vitro experiments alone}. From the electrophysiological experiment, pathological electrical signaling can be observed through measurements of APs at the whole-cell level and currents at the ion-channel level. However, it is difficult to relate, rigorously, the impacts of VGIC gating changes to the altered AP waveform/conduction and vice versa. 2) \textit{Segregating different $\text{K}^{+}$ currents ($\text{I}_{K}$) is difficult using whole-cell recording experimental techniques only}. $\text{I}_{Ksum}$ is the result of activity of multiple isoforms with each isoform producing a different, but slightly overlapping (in activation and inactivation voltages) component of the total $\text{K}^{+}$ current ($\text{I}_{Ksum}$) \cite{du2017} that thereby contributes to various portions of AP repolarization. However, in-vitro experiments can only measure the sum of these component currents ($\text{I}_{Ksum}$) using whole-cell voltage-clamp protocols. Even pharmacologic separation of $\text{K}_{v}$ current types is difficult, as the specificity of drugs for a single current type is not ideal. Therefore, component $\text{K}^{+}$ currents are usually estimated through multiple exponential fits of the decaying portion (due to channel inactivation) of the total $\text{K}^{+}$ current \cite{brunet2004heterogeneous}. Although the exponential function illustrates the shape of a component-current trace well, it cannot adequately describe kinetic dynamics of the current, nor fully and rigorously distinguish among currents produced by different $\text{K}_{v}$ isoforms because of their slightly overlapping voltage-dependence of gating. As $\text{K}_{v}$ have a critical function in repolarizing the cell, it is imperative to model and examine $\text{K}_{v}$ isoform thoroughly.

Therefore, this paper presents simulation modeling of dominant $\text{K}^{+}$ currents in mouse ventricular myocytes and further calibrate their parameters using the in-vitro data under normal and reduced glycosylation conditions through ablation of the Mgat1 gene. Calibrated models help describe key characteristics of glycosylation effects and data recorded from in-vitro experiments \cite{ednie2019reduced}. Specifically, we propose an optimization procedure to calibrate simulation models of potassium channel isoform activity, $\text{I}_{Kto}$ and $\text{I}_{Kslow}$, in mouse cardiomyocytes.  Fig. 3 shows  major component $\text{K}^{+}$ currents, including $\text{I}_{Ksum}$, $\text{I}_{Kto}$, $\text{I}_{Kslow}$ and $\text{I}_{Kss}$. Key characteristics of component currents, amplitudes, and inactivation rates ($\tau$'s) are measured from in-vitro experimental data with a 4.5 s voltage-clamp protocol (see details in Section III). The major contributions of this paper are summarized as follows.
\begin{itemize}
    \item Simulation models are integrated with in-vitro experiments to investigate the effects of reduced N-glycosylation on $\text{K}_{v}$ activity of mouse myocytes. Computer simulation helps demonstrate the voltage-gating mechanism and conductance kinetics that cannot be readily available through traditional exponential models. 
    \item A self-breeding Genetic Algorithm procedure is developed to calibrate simulation models of voltage-gated $\text{K}^{+}$ channel of mouse ventricular apex myocytes based on key statistics and raw data obtained from in-vitro experiments.
    \item Calibrated models facilitate the prediction of $\text{K}_{v}$ characteristics at different voltages that are not observed in the in-vitro experiments. In the Mgat1KO group, both $\text{I}_{Kto}$ and $\text{I}_{Kslow}$ densities are shown to be significantly reduced and the rate of $\text{I}_{Kslow}$ inactivation is much slower.
    \item Simulation modeling of cardiac myocytes is conducive to gain a better understanding of detailed $\text{K}_{v}$ kinetics, as well as how reduced glycosylation through  ablation of Mgat1 gene impacts $\text{K}_{v}$ kinetics.
\end{itemize}

@@

\subsection{Simulation Modeling of Mouse Ventricular Myocytes}
Electrophysiology was pioneered by Hodgkin and Huxley with a series of well-known experiments on the squid giant axon \cite{hodgkin1952quantitative}. Their simulation model was built upon two fundamental principles observed in the experimental data. 1) Cells are selectively activated by different ion channels. 2) Activities of ion channels to produce ionic currents are controlled through voltage changes, from which the name ``voltage-gated ion channels'' originates. The voltage-gating mechanism is embedded in the simulations model by partial differential equations. Not only are simulation models compatible with data and descriptive, but they also simulate changes of action potential waveforms, and cell conductance. Thus, models provide connections among ionic currents, action potentials, and conductance. However, significant domain knowledge in kinetics of ion channels and trial-and-error investigations are required, as advanced cardiomyocyte simulation models have complex structures based on nonlinear functions and differential equations with a high-dimensional set of parameters.

In the literature, optimization procedures have been proposed to fit cardiomyocyte simulation models to electrophysiological experimental data in an autonomous way as much as possible. $\text{Na}_{v}$ activity was coupled with in-vitro data of mouse cardiomyocyte using fractional factorial design and a Gaussian process model \cite{du2015statistical}. Fractional factorial designs were used to find significant control variables from the entire set of tuning parameters to reduce dimensionality. The Gaussian process model, which is computationally cheaper than the original $\text{Na}_{v}$ model, has served as a surrogate model to find optimal parameters. Characteristic curves such as steady-state activation (SSA), steady-state inactivation (SSI), and time constant of inactivation at different voltage were used to calculate goodness-of-fit as an objective function of optimization to minimize discrepancies with in-vitro experiment data. However, they are derived from current traces recorded during in-vitro experiments and may not always be available. For example, in our Mgat1KO data, currents were too small at early-activating voltages to reliably calculate the characteristic statistics.

\subsection{$\text{K}_{v}$ Isoforms}
\begin{figure}
    \label{fig3}
    \centering
    \includegraphics[width=0.8\linewidth]{photo/k_decomp_eg.png}
    \caption{Example of $\text{K}^{+}$ current decomposition into three component currents. Each component $\text{K}^{+}$ current has different characteristics in terms of their peak and decaying phase}
\end{figure}
The orchestrated activity of different $\text{K}_{v}$ isoforms produces multiple component currents, as illustrated in Fig. 1-(b). However, it is difficult to rigorously delineate the multiple component $\text{K}^{+}$ currents through voltage-clamp experiments alone as the sum of $\text{K}^{+}$ currents is measured \cite{brouillette2004functional}. Thus, $\text{I}_{Ksum}$ is usually decomposed mathematically by fitting the peak and decaying portion of each component current trace with an exponential function \cite{brunet2004heterogeneous}. As given in Equation (1), a standard exponential function has three parameters: amplitude ($\text{A}$), time constant ($\tau$), and constant offset value $\text{C}$. $t$ is time in millisecond. Amplitude refers to the value of the peak and $\tau$ to the time constant when current reduces by $e^{-1}$ (~63\%) of the peak.

@@

% === IV. RESEARCH METHODOLOGY ==========================================
% =======================================================================
\section{Research Methodology}
In this study, we propose an optimization procedure to calibrate simulation models of potassium channel isoform activity in mouse cardiomyocytes. Coupling in-vitro data of $\text{K}_{v}$ with a simulation model has advantages that a bi-exponential function cannot provide. For example, ionic currents, action potentials, and conductance can be determined more rigorously; and models allow for the simulation of conditions different from those used in the in-vitro experiment.

@@

\subsection{Optimization Process}
\begin{figure}
    \label{fig5}
    \centering
    \includegraphics[width=1\linewidth]{photo/algorithm.png}
    \caption{An illustration of proposed self-breeding genetic algorithm and comparison with standard genetic algorithm}
\end{figure}
Due to the nonlinear structure and differential equations involved in $\text{K}^{+}$ current models, it is difficult to use classical linear/nonlinear optimization methods. We proposed a novel metaheuristics optimization method based on the genetic algorithm (GA). Metaheuristics optimization is a higher-level procedure, which means that it is not problem-specific, but to find sufficiently satisfactory solutions for complex optimization problems to which it is difficult to apply traditional mathematical optimization algorithms \cite{boussaid2013survey}. Most metaheuristics methods have common characteristics: they are inspired by nature, for example, natural selection (genetic algorithm) and behavior of an ant colony (ant colony algorithm); they involve local-search heuristic methods without gradient or Hessian matrix. GA mimics the evolution of genes based on natural selection \cite{holland1992adaptation}, and its procedure is described in Algorithm 1.
\begin{algorithm}
    \caption{Standard Genetic Algorithm}
    \begin{algorithmic}[1]
        \renewcommand{\algorithmicrequire}{\textbf{Input:}}
        \renewcommand{\algorithmicensure}{\textbf{Output:}}
        \REQUIRE Stopping criterion, Population size $N$, Number of solutions to be selected $k$
        \ENSURE Best solution $\mathbf{x^*} \in \mathbb{R}^n$
        \\ \textit{Initialization}:
        \STATE Generate a random initial population of size $N$
        \\ \textit{LOOP Process}
        \WHILE{Satisfying stopping criterion}
        \STATE Fitness - Evaluate fitness of each solution in current population
        \STATE Selection - Select $k$ solutions with highest fitness and update best solution $\mathbf{x^{*}}$
        \STATE Breeding - Generate additional $N-k$ new solutions by doing crossover elements of top $k$ solutions randomly
        \STATE Mutation - Add random noise 
        \STATE Update current population with solutions generated through Step 4 and Step 6
        \ENDWHILE
        \RETURN $\mathbf{x^{*}}$ 
    \end{algorithmic} 
\end{algorithm}

In the standard GA, a new population is constructed from top solutions of the previous population and new solutions reproduced in Breeding step by so-called crossover. As illustrated in Fig. 5, the crossover is a process of mixing up elements of superior solutions in the current population so that this process is also called reproduction. It is expected to discover better candidates for combinatorial optimization problems by searching combinations of elite solutions. Although crossover is an intuitive searching method for combinatorial or discrete optimization problems, exploring combinations is not appropriate for continuous variables. Hence, in this paper, we presented a new method named \textit{self-breeding genetic algorithm} that reproduces new generations without crossover but directly breeds them from each superior solution. The procedure is described in Algorithm 2, and Fig. 5 illustrates the difference between standard GA and proposed \textit{self-breeding GA}.
\begin{algorithm}
    \caption{Self-breeding Genetic Algorithm}
    \begin{algorithmic}[1-=0+-*]
        \renewcommand{\algorithmicrequire}{\textbf{Input:}}
        \renewcommand{\algorithmicensure}{\textbf{Output:}}
        \REQUIRE Tolerance $(\epsilon_{A}, \epsilon_{\tau})$, Target amplitude and time constant $(A, \tau)$, Population size $N$, Selection size $k$, Breeding size $s$, Lower bound $\mathbf{l} \in \mathbb{R}^p$, Upper bound $\mathbf{u} \in \mathbb{R}^p$
        \ENSURE Model discrepancy $(\delta_{A}, \delta_{\tau})$, Solution $\mathbf{x}^* \in \mathbb{R}^p$
        \\ \textit{Initialization}:
        \STATE Construct initial population by generating $N$ solutions from $Unif(\mathbf{l}, \mathbf{u})$
        \\ \textit{LOOP Process}
        \WHILE{$\delta_{A} \geq \epsilon_{A}$ and $\delta_{\tau} \geq \epsilon_{\tau}$}
        \STATE Fitness - Evaluate fitness of each solution in current population        
        \STATE Update $\delta_{A}$ and $\delta_{\tau}$
        \STATE Selection - Select $k$ solutions $\mathbf{x_i}$, $i=1,2,...,k$, with highest fitness and update best solution $\mathbf{x^{*}}$
        \STATE Calculate variance $\mathbf{\sigma}^2$ of top $k$ solutions
        \FOR {$i = 1$ to $k$}
            \STATE Generate $s$ solutions of $\mathbf{x_i} + N(0,\mathbf{\sigma}^2)$
        \ENDFOR
        \STATE Update current population with top $k$ solutions generated in Step 4 and $ks$ solutions generated through Step 6 and Step 8
        \ENDWHILE
        \RETURN $(\delta_{A}, \delta_{\tau})$ and $\mathbf{x}^*$
    \end{algorithmic} 
\end{algorithm}

>>>>

% === ABSTRACT ==========================================================
% =======================================================================
\begin{abstract}
Cardiovascular disease is a leading cause of death worldwide. Dilated cardiomyopathy (DCM) is the third most common cause of heart failure and the most frequent reason for heart transplantation; upward of 70\% of DCM cases are considered idiopathic. We showed, through in-vitro experiments, that reduced hybrid/complex N-glycosylation in mouse cardiomyocytes is sufficient to cause DCM. Further, we investigated the role of reduced complex N-glycosylation in the gating and activities of voltage-gated ion channels, specifically, $\text{Na}^{+}$ ($\text{Na}_{v}$), $\text{Ca}^{2+}$ ($\text{Ca}_{v}$), and $\text{K}^{+}$ ($\text{K}_{v}$) channels responsible for ventricular myocyte action potentials (APs). In addition to direct effects of reduced N-glycosylation on $\text{Na}_{v}$ and $\text{Ca}_{v}$ gating, we observed aberrant electrical signalings such as prolonged APs and abnormal early re-activations, consistent with an observed reduction in $\text{K}_{v}$ expression and activity. However, it is difficult to rigorously determine the effects of reduced hybrid/complex N-glycosylation on $\text{K}_{v}$ activity, as there are multiple isoforms in the mouse ventricle including, $\text{K}_{v}1.5$, $\text{K}_{v}2.1$, and $\text{K}_{v}4.2$, that collectively produce the repolarizing phase of the AP. Because of the unique inactivation kinetics of $\text{K}_{v}$ isoforms, only the sum of $\text{K}^{+}$ currents ($\text{I}_{Ksum}$) can be recorded experimentally and decomposed later using exponential fitting to estimate component currents flowing through $\text{K}_{v}$ isoforms. This decomposition does not consider kinetics of $\text{K}_{v}$ under different glycosylation conditions. Here, we propose to develop simulation models for dominant $\text{K}^{+}$ currents in mouse ventricular myocytes and calibrate their parameters using the in-vitro data under normal and reduced glycosylation conditions through ablation of the Mgat1 gene. Calibrated models help describe key characterisitcs of glycosylation effects on gating and activities of $\text{K}_{v}$. A novel model calibration procedure is proposed to deal with complex ionic current models based on nonlinear functions and differential equations. Experimental results show that the proposed method has strong potential to calibrate complex simulation models with sparse data and predict characteristics of multiple $\text{K}_{v}$ isoforms to understand detailed kinetics.
\end{abstract}

% === KEYWORDS ==========================================================
% =======================================================================
\begin{IEEEkeywords}
Electrophysiology, N-glycosylation, dilated cardiomyopathy, potassium channel, simulation modeling, genetic algorithm. 
\end{IEEEkeywords}

@@

Thus, we investigated the impact of reduced hybrid/complex N-glycosylation through the lens of electrophysiology. Electrophysiology refers to studies of electrical properties in cells, tissues, or organs, including the examination of voltage, currents, and changes in scales from ion channels to organ systems \cite{scanziani2009electrophysiology}. Electrical signaling in the heart has vital functions related to intra and extracellular communication, rhythmicity of heartbeats, and provides a driving force for contraction. The action potential (AP) is the net transmembrane potential varying over time which results from the composite activities of different ion channels \cite{grant2009cardiac}. Fig. 1-(a) shows the simulated AP of a mouse ventricular apex myocyte using models adopted from \cite{bondarenko2004computer}. The AP is the result of orchestrated activities of various ionic currents described in Fig. 1-(b). Even small changes in VGIC's function can contribute to aberrant AP waveform and/or conduction, leading to arrhythmias. As illustrated in Fig. 2, $\text{Na}^{+}$ channels ($\text{Na}_{v}$) are responsible for AP initiation, or the depolarization phase, $\text{Ca}^{2+}$ channels ($\text{Ca}_{v}$) drives the prolonged depolarization phase particularly in larger species (“plateau”), while several $\text{K}^{+}$ channel ($\text{K}_{v}$) isoforms are collectively responsible for AP deactivation, i.e., repolarization. Like most transmembrane proteins, VGICs are heavily glycosylated membrane proteins \cite{ednie2011modulation}. Studies have proven that glycosylation can affect VGIC function predominantly. For example, we reported that a saturating, electrostatic effect of negatively charged sialic acids, which are typically attached to the terminal of glycan branches, significantly altered cardiac electrical signaling \cite{ednie2013expression, ednie2015reduced}. Our recent studies observed aberrant electrical signaling, e.g., prolonged APs and abnormal early re-activations, in Mgat1KO ventricular apex myocytes \cite{ednie2019reduced, ednie2019reduced2}. These observations strongly support direct and disease-related effects of reduced N-glycosylation on VGIC gating and activity.
\begin{figure}
    \label{fig1}
    \centering
    \subfloat[]{\includegraphics[width=0.8\linewidth]{photo/sim_ap.png}}
    \\
    \subfloat[]{\includegraphics[width=0.8\linewidth]{photo/sim_currents.png}}
    \caption{Simulation results of the (a) action potential and (b) relevant ionic currents (i.e., $\text{I}_{Kto}$, $\text{I}_{Kslow}$, $\text{I}_{Kss}$, $\text{I}_{Na}$, and $\text{I}_{CaL}$) of mouse ventricular myocytes. Potassium currents have positive currents, while sodium and calcium currents are negative.}
\end{figure}

\begin{figure}
    \label{fig2}
    \centering
    \includegraphics[width=0.8\linewidth]{photo/ap_ion_channels.png}
    \caption{Predominant ion channels in human ventricular myocytes and their functional role in shaping an AP.}
    \label{fig:my_label}
\end{figure}

Although these in-vitro experiments showed changes in activities of ion channels, there are certain limitations that include: 1) \textit{Detailed ion channel kinetics are difficult to determine rigorously using in-vitro experiments alone}. From the electrophysiological experiment, pathological electrical signaling can be observed through measurements of APs at the whole-cell level and currents at the ion-channel level. However, it is difficult to relate, rigorously, the impacts of VGIC gating changes to the altered AP waveform/conduction and vice versa. 2) \textit{Segregating different $\text{K}^{+}$ currents ($\text{I}_{K}$) is difficult using whole-cell recording experimental techniques only}. $\text{I}_{Ksum}$ is the result of activity of multiple isoforms with each isoform producing a different, but slightly overlapping (in activation and inactivation voltages) component of the total $\text{K}^{+}$ current ($\text{I}_{Ksum}$) \cite{du2017} that thereby contributes to various portions of AP repolarization. However, in-vitro experiments can only measure the sum of these component currents ($\text{I}_{Ksum}$) using whole-cell voltage-clamp protocols. Even pharmacologic separation of $\text{K}_{v}$ current types is difficult, as the specificity of drugs for a single current type is not ideal. Hence, component $\text{K}^{+}$ currents are usually estimated through multiple exponential fits of the decaying portion (due to channel inactivation) of the total $\text{K}^{+}$ current \cite{brunet2004heterogeneous}. Although the exponential function illustrates the shape of a component-current trace well, it cannot adequately describe kinetic dynamics of the current, nor fully and rigorously distinguish among currents produced by different $\text{K}_{v}$ isoforms because of their slightly overlapping voltage-dependence of gating. As $\text{K}_{v}$ have a critical function in repolarizing the cell, it is imperative to model and examine $\text{K}_{v}$ isoform thoroughly.

Therefore, this paper presents simulation modeling of dominant $\text{K}^{+}$ currents in mouse ventricular myocytes and further calibrate their parameters using the in-vitro data under normal and reduced glycosylation conditions through ablation of the Mgat1 gene. Calibrated in-silico models help describe and predict gaing kinetics and channel activities of glycosylation effects and data recorded from in-vitro experiments \cite{ednie2019reduced}. Specifically, we propose an optimization procedure to calibrate simulation models of potassium channel isoform activity, $\text{I}_{Kto}$ and $\text{I}_{Kslow}$, in mouse cardiomyocytes.  Fig. 3 shows  major component $\text{K}^{+}$ currents, including $\text{I}_{Ksum}$, $\text{I}_{Kto}$, $\text{I}_{Kslow}$ and $\text{I}_{Kss}$. Key characteristics of component currents, amplitudes, and inactivation rates ($\tau$'s) are measured from in-vitro experimental data with a 4.5 s voltage-clamp protocol (see details in Section III). The major contributions of this paper are summarized as follows.
\begin{itemize}
    \item Simulation models are integrated with in-vitro experiments to investigate the effects of reduced N-glycosylation on $\text{K}_{v}$ activity of mouse myocytes. Computer simulation helps demonstrate the voltage-gating mechanism and conductance kinetics that cannot be readily available through traditional exponential fitting. 
    \item A self-breeding Genetic Algorithm procedure is developed to calibrate simulation models of voltage-gated $\text{K}^{+}$ channel of mouse ventricular apex myocytes based on key characterisitcs and raw data obtained from in-vitro experiments.
    \item Calibrated models facilitate the prediction of $\text{K}_{v}$ characteristics at different voltages that are not observed in the in-vitro experiments. In the Mgat1KO group, both $\text{I}_{Kto}$ and $\text{I}_{Kslow}$ densities are shown to be significantly reduced and the rate of $\text{I}_{Kslow}$ inactivation is much slower.
    \item Simulation modeling of cardiac myocytes is conducive to gain a better understanding of detailed $\text{K}_{v}$ kinetics, as well as how reduced glycosylation through ablation of Mgat1 gene impacts $\text{K}_{v}$ kinetics.
\end{itemize}

@@

\subsection{Simulation Modeling of Mouse Ventricular Myocytes}
Electrophysiology was pioneered by Hodgkin and Huxley with a series of well-known experiments on the squid giant axon to investigate action potentials in neurons \cite{hodgkin1952quantitative}. Their simulation model was built upon two fundamental principles observed in the experimental data. 1) Cells are selectively activated by different ion channels. 2) Activities of ion channels to produce ionic currents are controlled through voltage changes, from which the name ``voltage-gated ion channels'' originates. These biophysical principles of VGICs that are encoded in terms of mathematical equations. These principles are general for cardiomyocytes under different experimental conditions, e.g., genetic or pharmaceutical perturbations, but the equations should be calibrated to the conditions. However, calibrating simulation models to couple with experimental data requires trial-and-error investigations and domain knowledge in both the kinetics of cardiomyocytes and mathematics of computer models.

In the literature, optimization procedures have been proposed to fit cardiomyocyte simulation models to electrophysiological experimental data in an autonomous way as much as possible. $\text{Na}_{v}$ activity was coupled with in-vitro data of mouse cardiomyocyte using fractional factorial design and a Gaussian process model \cite{du2015statistical}. Fractional factorial designs were used to find significant control variables from the entire set of tuning parameters to reduce dimensionality. The Gaussian process model, which is computationally cheaper than the original $\text{Na}_{v}$ model, has served as a surrogate model to find optimal parameters. Characteristic curves such as steady-state activation (SSA), steady-state inactivation (SSI), and time constant of inactivation at different voltage were used to calculate goodness-of-fit as an objective function of optimization to minimize discrepancies with in-vitro experiment data. However, they are derived from current traces recorded during in-vitro experiments and may not always be available. For example, in our Mgat1KO data, currents were too small at early-activating voltages to reliably calculate the characteristic curves.

\subsection{$\text{K}_{v}$ Isoforms}
\begin{figure}
    \label{fig3}
    \centering
    \includegraphics[width=0.8\linewidth]{photo/k_decomp_eg.png}
    \caption{Example of $\text{K}^{+}$ current decomposition into three component currents. Each component $\text{K}^{+}$ current has different characteristics in terms of their peak and decaying phase.}
\end{figure}
The orchestrated activity of different $\text{K}_{v}$ isoforms produces multiple component currents, as illustrated in Fig. 1-(b). However, it is difficult to rigorously delineate the multiple component $\text{K}^{+}$ currents through voltage-clamp experiments alone as the sum of $\text{K}^{+}$ currents is measured \cite{brouillette2004functional}. Thus, $\text{I}_{Ksum}$ is usually decomposed mathematically by fitting the peak and decaying portion of each component current trace with an exponential function \cite{brunet2004heterogeneous}. As given in Equation (1), a standard exponential function has three parameters: amplitude ($\text{A}$), time constant ($\tau$), and constant offset value $\text{C}$. $t$ is time in millisecond. Amplitude refers to the value of the peak and $\tau$ to the time constant when current reduces by $e^{-1}$ (~63\%) of the peak.

@@

% === IV. RESEARCH METHODOLOGY ==========================================
% =======================================================================
\section{Research Methodology}
In this study, we propose an optimization procedure to calibrate simulation models of potassium channel isoform activity in mouse cardiomyocytes. Coupling in-vitro data of $\text{K}_{v}$ with in-silico models has advantages that bi-exponential fitting cannot provide. For example, ionic currents, action potentials, and conductance can be determined more rigorously; and models allow for the simulation of conditions different from those used in the in-vitro experiment.

@@

\subsection{Optimization Process}
\begin{figure}
    \label{fig5}
    \centering
    \includegraphics[width=1\linewidth]{photo/algorithm.png}
    \caption{An illustration of proposed self-breeding genetic algorithm and comparison with standard genetic algorithm.}
\end{figure}
Running ion channel simulation models involves solving partial differential equations based on nonlinear functions, which is computationally costly. An efficient calibration framework is necessary to calibrate $\text{K}_{v}$ models. We proposed a novel metaheuristics optimization method based on the genetic algorithm (GA). Metaheuristics optimization is a higher-level procedure, which means that it is not problem-specific, but to find sufficiently satisfactory solutions for complex optimization problems efficiently \cite{boussaid2013survey}. Most metaheuristics methods have common characteristics: they are inspired by nature, for example, natural selection (genetic algorithm) and behavior of an ant colony (ant colony algorithm); they involve local-search heuristic methods without gradient or Hessian matrix. GA mimics the evolution of genes based on natural selection \cite{holland1992adaptation}, and its procedure is described in Algorithm 1.
\begin{algorithm}
    \caption{Standard Genetic Algorithm}
    \begin{algorithmic}[1]
        \renewcommand{\algorithmicrequire}{\textbf{Input:}}
        \renewcommand{\algorithmicensure}{\textbf{Output:}}
        \REQUIRE Stopping criterion, Population size $N$, Number of solutions to be selected $k$
        \ENSURE Best solution $\mathbf{x^*} \in \mathbb{R}^n$
        \\ \textit{Initialization}:
        \STATE Generate a random initial population of size $N$
        \\ \textit{LOOP Process}
        \WHILE{Satisfying stopping criterion}
        \STATE Fitness - Evaluate fitness of each solution in current population
        \STATE Selection - Select $k$ solutions with highest fitness and update best solution $\mathbf{x^{*}}$
        \STATE Breeding - Generate additional $N-k$ new solutions by doing crossover elements of top $k$ solutions randomly
        \STATE Mutation - Add random noise 
        \STATE Update current population with solutions generated through Step 4 and Step 6
        \ENDWHILE
        \RETURN $\mathbf{x^{*}}$ 
    \end{algorithmic} 
\end{algorithm}

In the standard GA, a new population is constructed from superior solutions of the current population and new solutions are reproduced in Breeding step by so-called crossover. As illustrated in Fig. 5, the crossover is a process of mixing up elements of superior solutions in the current population so that this process is also called reproduction. This procedure is expected to discover better candidates for combinatorial optimization problems by searching combinations of elite solutions. Although crossover is an intuitive searching method for combinatorial or discrete optimization problems, exploring combinations is not appropriat0e for continuous variables. Hence, in this paper, we presented a new method named \textit{self-breeding genetic algorithm} that reproduces new generations without crossover but directly breeds them from each superior solution. The procedure is described in Algorithm 2, and Fig. 5 illustrates the difference between standard GA and proposed \textit{self-breeding GA}.
\begin{algorithm}
    \caption{Self-breeding Genetic Algorithm}
    \begin{algorithmic}[1-=0+-*]
        \renewcommand{\algorithmicrequire}{\textbf{Input:}}
        \renewcommand{\algorithmicensure}{\textbf{Output:}}
        \REQUIRE Tolerance $(\epsilon_{A}, \epsilon_{\tau})$, Target amplitude and time constant $(A, \tau)$, Population size $N$, Selection size $k$, Breeding size $s$, Lower bound $\mathbf{l} \in \mathbb{R}^p$, Upper bound $\mathbf{u} \in \mathbb{R}^p$
        \ENSURE Model discrepancy $(\delta_{A}, \delta_{\tau})$, Solution $\mathbf{x}^* \in \mathbb{R}^p$
        \\ \textit{Initialization}:
        \STATE Construct initial population by generating $N$ solutions from $Unif(\mathbf{l}, \mathbf{u})$
        \\ \textit{LOOP Process}
        \WHILE{$\delta_{A} \geq \epsilon_{A}$ and $\delta_{\tau} \geq \epsilon_{\tau}$}
        \STATE Fitness - Evaluate fitness of each solution in current population        
        \STATE Update $\delta_{A}$ and $\delta_{\tau}$
        \STATE Selection - Select $k$ solutions $\mathbf{x_i}$, $i=1,2,...,k$, with highest fitness and update best solution $\mathbf{x^{*}}$
        \STATE Calculate variance $\mathbf{\sigma}^2_{i}$ of top $k$ solutions and calculate pooled variance $\mathbf{\sigma}_{p}$ using recent $w$ recent variances, $\mathbf{\sigma}^2_{i}$, $\mathbf{\sigma}^2_{i-1}$, ..., $\mathbf{\sigma}^2_{i-w+1}$
        \FOR {$i = 1$ to $k$}
            \STATE Generate $s$ solutions of $\mathbf{x_i} + N(0,\mathbf{\sigma}^2)$
        \ENDFOR
        \STATE Update current population with top $k$ solutions generated in Step 4 and $ks$ solutions generated through Step 6 and Step 8
        \ENDWHILE
        \RETURN $(\delta_{A}, \delta_{\tau})$ and $\mathbf{x}^*$
    \end{algorithmic} 
\end{algorithm}
